\cvsection{Projects}
\begin{cventries}
  \cventry
    {Guide – Prof. Mukesh Goswami | DEPARTMENT OF INFORMATION AND TECHNOLOGY}
    {Stock Predicter | Platform- Django, Python}
    {Team of 3}
    {July. 2018 - Exp. Dec. 2018}
    {
      \begin{cvitems}
        \item {Task – Web Application to predict stock of Tomorrow with Candlesticks and news and twitter analysis of Current Trends.}
        \item {Role –  Lead The Team by Creating the Djnago GUI and Test RNN,Exponential Models to predict the future stock of next Day}
        \item {Result –  Combining the news and twitter 3rd Degree Regression provide much greater chance to predict the stock of future.}
      \end{cvitems}
    }
  \cventry
    {Guide – Prof. Archna Vyas | Student Startup and Innovation Policy INDIA. }
    {Hackathon | Platform- Phpmyadmin, php, Aws}
    {Team of 8}
    {Oct. 2017 - March. 2018}
    {
      \begin{cvitems}
        \item {Task – Web Portal to find meritorious students of Gujarat in primary school (around 90 lac entry).}
        \item {Role – Was Part of Front-end team and created Core PHP pages and Also managed Aws S3 bucket to upload Student images and integrated  Web-app to Aws mysql to portability and efficiency}
        \item {Result – Only Team that Won Regional Round with same Topic, Runners up at states level.}
        \end{cvitems}
    }
  \cventry
    {Guide – Prof. Roshni Raval | DEPARTMENT OF INFORMATION AND TECHNOLOGY}
    {Prison Management System | Platform- Phpmyadmin,php}
    {Team of 2}
    {July 2017 - Nov. 2017}
    {
      \begin{cvitems}
        \item {Task – to create Management system that can handle prisoners, warden, requests to meet prisoner, and all Crud Operations.}
      \end{cvitems} 
    }
  \cventry
    {Udemy Course}
    {Vidjot - Note taking System  self | Platform - Mean stack}
    {Self}
    {Jul. 2012 - Jun. 2013}
    {
      \begin{cvitems}
                \item {Task – build platform to upload notes online.}
                \item {Learned - Basics of MEAN Stack.}
                \item {Learned - Crud Operation of MEAN Stack.}
                \item {Learned - Heroku Platform | Deployment.}
                \item {Learned - Workaround with MongoDB.}
            \end{cvitems}
    }  
  \cventry
    {Guide – Prof. R.S Chhajad | DEPARTMENT OF INFORMATION AND TECHNOLOGY}
    {Multilevel Car Parking System | Platform- Assembly Language}
    {Self}
    {Dec. 2011 - Feb. 2012}
    {
      \begin{cvitems}
        \item {Task – If any level have empty space for car to park it will show green color. }
        \item {Task – User can park there cars at any of given level. }
        \item {Task – If any of given level are full show red color to indicates that particular level is full.}
      \end{cvitems}
    }
    \cventry
    {Guide – prof rina desai}
    {Energy - Explore Harness and Conserve | Research Presentation}
    {Team of 3}
    {Dec. 2011 - Feb. 2012}
    {
      \begin{cvitems}
        \item {....}
      \end{cvitems}
    }
\end{cventries}
